Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-19 Codes/PrepareResults.rmd
made changes for publication

```{r, dependson = "setup"}
field_Ndesign <-
  ggplot() +
  geom_sf(
    data = field_plot_sf,
    aes(fill = factor(rate)), size = 0,
    inherit.aes = FALSE,
  ) +
  scale_fill_viridis_d() +
  labs(fill = "Nitrogen rate\n  (kg/ha)") +
  ggtitle("(1) Trial Design") +
  theme_figure
```

@@

```{r, dependson = "setup"}
# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield Level\n  (kg/ha)") +
  ggtitle("(2) Simulated Yield Level") +
  theme_figure
```

@@

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
  na.omit() %>%
  dplyr::rename(tgtn = NPlan, tgts = SRPlan)

data_dt <- data.table(data_sf) %>%
  setnames(names(.), tolower(names(.)))

@@

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)
```

>>>>

```{r, dependson = "setup"}
field_Ndesign <-
  ggplot() +
  geom_sf(
    data = field_plot_sf,
    aes(fill = factor(rate)), size = 0,
    inherit.aes = FALSE,
  ) +
  scale_fill_viridis_d() +
  labs(fill = "Nitrogen rate\n  (kg/ha)") +
  ggtitle("(1) Trial design") +
  theme_figure
```

@@

```{r, dependson = "setup"}
# === subplot-level === #
vis_yield_subplot <-
  ggplot(field_subplot_sf) +
  geom_sf(aes(fill = yield), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = "Yield level\n  (kg/ha)") +
  ggtitle("(2) Simulated yield level") +
  theme_figure
```

@@

# data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
#   na.omit() %>%
#   dplyr::rename(tgtn = NPlan, tgts = SRPlan) %>%

# data_dt <- data.table(data_sf) %>%
#   setnames(names(.), tolower(names(.))) %>%
#   .[,.(tgts, yield, slope, ecs)]

# saveRDS(data_dt, here("Shared/Results/for_writing/ctree_data.rds"))

data_dt <- readRDS(here("Shared/Results/for_writing/ctree_data.rds"))

@@

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)
# fancyRpartPlot(opfit, sub="")
```

### 2022-02-19 Writing/CEA_2nd_round/replies_rev_1.rmd
made changes for publication

We do see a redundancy in our explanation of how CF can be used to identify site-specific input recommendations. It was explained twice, once each in subsections 2.2 and 3.2.2. We have deletedthe explanation in 2.2 and also changed the heading in 2.1 to "Estimating EOIR and Treatment Effects."

@@

Second, we consolidated subsection 3.1.4 and 3.1.5 of the original manuscript into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we removed some text and combined the original manuscript's figures x and y in the single figure z in the current manuscript.

Third, we moved to an appendix the previous manuscript’s detailed description of parameter splitting.

@@

<span style="color:blue">  
Done
</span>

@@

<span style="color:blue">  
Done. Please see Figure 2. 
</span>

@@

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (Table 1). Therefore, we thought that visualizing the CNN results would not provide much insight. However, we have decided to include CNN results in Figures 8, 9, and 10 of the previous manuscript. which are Figures 3, 4, and 5 of the revised manuiscript.

>>>>

We do see a redundancy in our explanation of how CF can be used to identify site-specific input recommendations. It was explained twice, once each in subsections 2.2 and 3.2.2. We have deletedthe explanation in 2.2 and also changed the heading in 2.1 to "EOIR Estimation and Treatment Effects."

@@

Second, we consolidated subsection 3.1.4 and 3.1.5 of the original manuscript into a single subsubsection called "Trial Design and Yield Data Generation for Modeling." In doing so, we removed some text and combined the original manuscript's figures 5 and 7 in the single figure 2 in the current manuscript.

Third, we moved to Appendix C.2 the previous manuscript’s detailed description of parameter splitting.

@@

<span style="color:blue">  
We modified the length units (line 162) 
</span>

@@

<span style="color:blue">  
We modified the figure. Please see Figure 1. 
</span>

@@

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (Table 1). Therefore, we thought that visualizing the CNN results would not provide much insight. However, we have decided to include CNN results in Figures 8, 9, and 10 of the previous manuscript. which are Figures 3, 4, and 5 of the revised manuscript.

### 2022-02-19 Writing/manuscript_cea.rmd
made changes for publication

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR. Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

>>>>

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR. Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. In the rounds in which BRF predicted yield best, then the two-step process worked well. For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.
